Testing out AdaPT

### 2017-12-08 datasets/GSEA/gsea.Rmd

>>>>

Plotting the methods overlap

sGSEASub <- sGSEA[,!apply( is.na( assays(sGSEA)[["qvalue"]] ), 2, all )]
sGSEASub <- sGSEASub[,-which(grepl("ihw", colData( sGSEASub )$blabel) & colData( sGSEASub )$param.alpha != 0.1)]
sGSEASub <- sGSEASub[,-which( grepl("bl", colData( sGSEASub)$blabel) & 
                   colData(sGSEASub)$param.smooth.df != 2L )]
sGSEASub <- sGSEASub[,!colData(sGSEASub)$blabel %in% "unadjusted"]

plotMethodsOverlap(sGSEASub, order.by = "freq", nsets=10)

### 2017-12-08 datasets/simulations/analysis-01-plot.Rmd
Move t-test sim summary parsing from 01 to 03

```{r, load-libraries, message=FALSE}
library("dplyr")
library("ggplot2")
library("viridis")
library("data.table")
library("SummarizedBenchmark")
```

@@

```{r}
## list of results from 100 replication experiments
dl <- list.dirs("data-tsim/M1", recursive=FALSE, full.names=TRUE)

@@

```{r}
## list of results from 100 replication experiments
dl <- list.dirs("data-tsim/M100", recursive=FALSE, full.names=TRUE)

for (dd in dl) {
    fl <- list.files(dd, pattern=".rds", full.names=TRUE)

>>>>

```{r, load-libraries, message=FALSE}
library("data.table")
library("SummarizedBenchmark")
library("tidyverse")
library("magrittr")
library("viridis")
library("cowplot")
```

@@

```{r}
## list of results from 100 replication experiments
dl <- c(list.dirs("data-tsim/M1", recursive=FALSE, full.names=TRUE),
        list.dirs("data-psim/M1", recursive=FALSE, full.names=TRUE))

@@

```{r}
## list of results from 100 replication experiments
dl <- c(list.dirs("data-tsim/M100", recursive=FALSE, full.names=TRUE),
        list.dirs("data-psim/M100", recursive=FALSE, full.names=TRUE))

for (dd in dl) {
    fl <- list.files(dd, pattern="M100\\.rds", full.names=TRUE)

### 2017-12-08 datasets/simulations/analysis-02-try-adapt.Rmd

```{r, fig.width = }
vec_tib %>%
    gather(var, value, -step) %>%
    ggplot(aes(x = step, y = value, label = step)) +
    geom_line(alpha = 1/2) + geom_point() +
    geom_text(vjust = 1/2, hjust = -0.5) + 
    facet_grid(var ~ ., scales = "free_y") +
    theme_bw()
```

>>>>

```{r, fig.width = 5, fig.height = 6}
vec_tib %>%
    gather(var, value, -step) %>%
    ggplot(aes(x = step, y = value, label = step)) +
    geom_line(alpha = 1/2) + geom_point() +
    geom_text(vjust = 1/2, hjust = -0.5) + 
    facet_grid(var ~ ., scales = "free_y") +
    theme_bw()
```
